\begin{thebibliography}{99}

\bibitem {bank}{\sc R.E. Bank}, {\em PLTMG: A Software Package for Solving
Elliptic Partial Differential Equations -- Users' Guide 7.0}, vol.
15, Frontiers in Applied Mathematics, SIAM Books, Philadelphia,
1994.

\bibitem{bramble}{\sc J.H. Bramble}, {\em Multigrid Methods}, vol. 294, Pitman
Research Notes in Mathematical Sciences, Longman Scientific and
Technical, Essex, England, 1993.

\bibitem{brandtmoc}{\sc A. Brandt}, {\em Multi-level adapative solutions to
boundary value problems}, Mathematics of Computation, 31, 1977,
pp. 333-390.

\bibitem{brandtguide}{\sc A. Brandt}, {\em Multigrid techniques: 1984 guide
with applications to fluid dynamics}, GMD-studien Nr. 85,
Gesellschaft f\"{u}r Mathematik und Datenverarbeitung, St.
Agustin, 1984.

\bibitem{brandtamg}{\sc A. Brandt}, {\em Algebraic multigrid theory: the symmetric case},
Appl. Math. Comput., 19, 1986, pp. 23-56.

\bibitem{brandtmr}{\sc A. Brandt, S.F. McCormick, J. Ruge}, {\em Algebraic multigrid (AMG) for sparse matrix equations}, in Sparsity and its Applications, D.J. Evans, ed., Cambridge University Press, 1984.

\bibitem{demmel}{\sc J.W. Demmel}, {\em Applied Numerical Linear Algebra},
SIAM, Philadelphia, 1997.

\bibitem{Dennis}{\sc J.E. Dennis and R.B. Schnabel}, {\em Numerical Methods for
Unconstrained Optimization and Nonlinear Equations}, SIAM Books,
Philadelphia, 1996.

\bibitem{golub}{\sc G. Golub and C. Van Loan}, {\em Matrix Computations},
Johns Hopkins University Press, 1996

\bibitem{hackbush}{\sc W. Hackbusch}, {\em Multigrid Methods and Applications},
vol. 4, Computational Mathematics, Springer-Verlag, Berlin, 1985.

\bibitem{hacktrot}{\sc W. Hackbusch and U. Trottenberg}, {\em Multigrid Methods},
vol. 960, Lecture Notes in Mathematics, Springer-Verlag, Berlin,
1982.

\bibitem{jespersen}{\sc D. Jespersen}, {\em Multigrid Methods for Partial
Differential Equations}, in Studies in Numerical Analysis, vol.
24, Studies of Mathematics, MAA, Washington D.C., 1984.

\bibitem{smfrontiers}{\sc S.F. McCormick}, ed., {\em Multigrid Methods}, vol. 3,
Frontiers in Applied Mathematics, SIAM Books, Philadelphia, 1987.

\end{thebibliography}
